{RandomPoints} package for \emph{Macaulay2}

### 2021-07-15 FastLinAlg/Paper/RandomRationalPoints.tex
Improvements to the paper.

    \item[\tt DecompositionStrategy]  Within the {\tt LinearIntersection} strategy, one can also specify the option {\tt DecompositionStrategy}.  Valid values are {\tt Decompose} and {\tt MultiplicationTable}, the latter of which is currently only implemented for homogeneous ideals.

@@

@@

    When calling {\tt randomPoints} with a {\tt BruteForce} strategy, this denotes the number of trials for brute force point checking.

@@

\begin{example} We illustrate the speed difference in this example.
	{\color{blue}{
			\begin{quote}
				\begin{verbatim}
i2 : S = ZZ/101[y_0..y_9];

@@

	o6 = | x-3 z-5 -x+3y-4z+2 |

	i7 : matrix randomCoordinateChange(R, MaxCoordinatesToReplace => 1, 
	Replacement => Binomial)

	o7 = | y x+4z z |
\end{verbatim}
\end{quote}
    }}

@@

            ZZ                                         2          2
o3 = (map(R,--[z, w],{- x - 2y - z, - y - 2z}), ideal(z  - z*w - w ))                   
            5
\end{verbatim}
\end{quote}
    }}
\end{example}\vspace{-1em}
Alternatively, instead of {$I$}, we may pass it a quotient ring.  It will then return the inclusion of the generic projection ring into the given ring, followed by the source of that inclusion.  It is essentially the same functionality as calling {\tt genericProjection(n, ideal R)} although the format of the output is slightly different.

@@

The user may also provide the following additional information:

\begin{description}
\item[\tt Strategy => Symbol] Specify a strategy to use when calling {\tt randomPoints} (see \Cref{strategydetails}).

\item[\tt Verbose => Boolean]
  Set the option {\tt Verbose => true} to turn on verbose output.  This may be useful in debugging or in determining why a computation is running slowly.

\item[\tt Homogeneous => Boolean] (see \Cref{helper})

\item[\tt MinorPointAttempts => ZZ] 
  This controls how many points at which to check the rank.
\end{description}
%\vspace{0.25em}
\begin{example}
  We demonstrate this function.
  {{\small\color{blue}
  \begin{quote}
\begin{verbatim}
		i3 : R = ZZ/5[x, y, z];

>>>>

    \item[\tt DecompositionStrategy]  Within the {\tt LinearIntersection} strategy, one can also specify the option {\tt DecompositionStrategy}.  Valid values are {\tt Decompose} and {\tt MultiplicationTable}, the latter of which is currently only implemented for homogeneous ideals.  Additionally, the {\tt Default} strategy switches back and forth between {\tt Decompose} and {\tt MultiplicationTable} for homogeneous ideals.  Setting this to {\tt Decompose} in the default strategy will force only {\tt Decompose} to be used.

@@

    \item[\tt Homogeneous]  Setting this true specifies that the origin (corresponding to the irrelevant ideal) is not a valid point.

@@

    When calling {\tt randomPoints} with a {\tt BruteForce} strategy, this denotes the number of trials for brute force point checking.  It also controls how many linear spaces to simultaneously study in the {\tt LinearIntersection} strategy.

@@

\begin{example} We illustrate the speed difference in this example.
	{\color{blue}{\small
			\begin{quote}
				\begin{verbatim}
i2 : S = ZZ/101[y_0..y_9];

@@

	o6 = | x-3 z-5 -x+3y-4z+2 |
\end{verbatim}
\end{quote}
    }}

@@

            ZZ                                         2          2
o3 = (map(R,--[z, w],{- x - 2y - z, - y - 2z}), ideal(z  - z*w - w ))                   
            5
\end{verbatim}
\end{quote}
    }}
\end{example}\vspace{-1em}
\noindent
Alternatively, instead of {$I$}, we may pass it a quotient ring.  It will then return the inclusion of the generic projection ring into the given ring, followed by the source of that inclusion.  %It is the same functionality as calling {\tt genericProjection(n, ideal R)} although the format of the output is slightly different.

@@

Besides the options from {\tt randomPoints} which are automatically passed to that function, the user may also provide the following additional information:

\begin{description}
    \item[\tt MinorPointAttempts => ZZ] 
  This controls how many points at which to check the rank.
\end{description}
%\vspace{0.25em}
\begin{example}
  We demonstrate this function.
  {{\small\color{blue}
  \begin{quote}
\begin{verbatim}
		i3 : R = ZZ/5[x, y, z];
